---
title: "Text Mining a Presidential Speech"
author: "Your Name"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-depth: 2
    number-sections: true
    code-fold: true
editor: visual
---

## 1. Load Required Libraries

```{r}
library(pdftools)
library(tidytext)
library(dplyr)
library(stringr)
library(ggplot2)
library(tidyr)
library(wordcloud)
library(igraph)
library(ggraph)
library(tm)
library(textdata)
```  

## 2. Read the PDF and Prepare the Text

```{r}
# Read PDF speech file
text <- pdf_text("presidential_speech.pdf")

# Collapse pages into one string
speech <- paste(text, collapse = " ")

# Create data frame
speech_df <- data.frame(text = speech, stringsAsFactors = FALSE)
```  

## 3. Tokenize and Remove Stop Words

```{r}
# Tokenize
tokens <- speech_df %>%
  unnest_tokens(word, text)

# Remove stop words
data("stop_words")
tokens_clean <- tokens %>%
  anti_join(stop_words, by = "word")
```  

## 4. Word Frequency Plot

```{r}
tokens_clean %>%
  count(word, sort = TRUE) %>%
  top_n(20) %>%
  ggplot(aes(reorder(word, n), n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 20 Most Common Words", x = NULL, y = "Frequency")
```  

## 5. Word Cloud

```{r}
library(RColorBrewer)
tokens_clean %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100, colors = brewer.pal(8, "Dark2")))
```  

## 6. Sentiment Analysis (Bing)

```{r}
bing_sentiments <- tokens_clean %>%
  inner_join(get_sentiments("bing"), by = "word")

bing_sentiments %>%
  count(sentiment, sort = TRUE) %>%
  ggplot(aes(x = sentiment, y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  labs(title = "Sentiment Counts")
```  

## 7. Bigram Network

```{r}
bigrams <- speech_df %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

bigrams_separated <- bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word, !word2 %in% stop_words$word)

bigram_counts <- bigrams_separated %>%
  count(word1, word2, sort = TRUE)

bigram_graph <- bigram_counts %>%
  filter(n > 3) %>%
  graph_from_data_frame()

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 3) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```  

## 8. TF-IDF Analysis by Paragraph

```{r}
speech_paragraphs <- data.frame(
  paragraph = unlist(strsplit(speech, split = "\n\n")),
  stringsAsFactors = FALSE
)

speech_paragraphs <- speech_paragraphs %>%
  mutate(id = row_number()) %>%
  unnest_tokens(word, paragraph) %>%
  anti_join(stop_words)

speech_paragraphs %>%
  count(id, word) %>%
  bind_tf_idf(word, id, n) %>%
  arrange(desc(tf_idf)) %>%
  top_n(15, tf_idf) %>%
  ggplot(aes(reorder(word, tf_idf), tf_idf, fill = factor(id))) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  labs(title = "Top TF-IDF Words by Paragraph")
```  

## 9. (Optional) Readability Metrics

```{r}
library(quanteda)
corp <- corpus(speech)
textstat_readability(corp, measure = "Flesch.Kincaid")
```  

## 10. (Optional) Topic Modeling (LDA)

```{r}
library(topicmodels)
dtm <- tokens_clean %>%
  count(word) %>%
  cast_dtm(document = 1, term = word, value = n)

lda_model <- LDA(dtm, k = 2, control = list(seed = 1234))
tidy(lda_model, matrix = "beta") %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  ggplot(aes(reorder(term, beta), beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
